Multiple regression: TRELIS-Q WP5 data

### 2024-04-02 Rmd/bookchapter.TRELIS-Q-WP5.Rmd
Lagre bilde til fil

---
title: "Multiple regression: TRELIS-Q WP5 data"
author: "Niklas Karlsen"
date: "2024-02-20"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true

@@

Sys.setenv(LANG = "no_NB.UTF-8")            # for norwegian æ,ø og å. Kilde:
Sys.setlocale("LC_ALL","Norwegian")
# https://stackoverflow.com/questions/16347731/how-to-change-the-locale-of-r
```

@@

@@

```{r}
ggplot(dc, aes(x=studiested2, y=var, fill=studiested2)) + 
  geom_bar(stat="identity", position="dodge") +
  #scale_fill_manual(values=viridis(3)) + 
  geom_errorbar(aes(ymin=var-sd, ymax=var+sd), # se
                  linewidth=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
  ggtitle("PCK, TK og TPACK fordelt på studiested") +
  guides(fill="none") +
  # https://stackoverflow.com/questions/53843221/make-y-axis-start-at-1-instead-of-0-within-ggplot-bar-chart
  coord_cartesian(ylim = c(1,5)) +
  ylab("verdi") +
  xlab("studiested gruppe") +
  theme_bw() +
  facet_wrap(~TPACK)
```

>>>>

---
title: "Multiple regression: TRELIS-Q WP5 data"
author: "Niklas Karlsen"
date: "2024-04-02"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true

@@

Sys.setenv(LANG = "no_NB.UTF-8")            # for norwegian æ,ø og å. Kilde:
Sys.setlocale("LC_ALL","Norwegian")
# https://stackoverflow.com/questions/16347731/how-to-change-the-locale-of-r

plot_to_file = 1
```

@@

Flytt origo

```{r}
data_trelis_q_ren[,unlist(TPACK_PST_list)] <- data_trelis_q_ren[,unlist(TPACK_PST_list)] - 3 
```

@@

```{r}
stolpediagram <- ggplot(dc, aes(x=studiested2, y=var, fill=studiested2)) + 
  geom_bar(stat="identity", position="dodge") +
  #scale_fill_manual(values=viridis(3)) + 
  geom_errorbar(aes(ymin=var-sd, ymax=var+sd), # se
                  linewidth=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
  ggtitle("PCK, TK og TPACK fordelt på studiested") +
  guides(fill="none") +
  # https://stackoverflow.com/questions/53843221/make-y-axis-start-at-1-instead-of-0-within-ggplot-bar-chart
#  coord_cartesian(ylim = c(1,5)) +
  ylab("verdi") +
  xlab("studiested gruppe") +
  theme_bw() +
  facet_wrap(~TPACK)

print(stolpediagram) # vis plot
```

```{r}
# save plot
if (plot_to_file) {
  ggsave("../output/TPACK_stolpediagram.png") #,height=8,width=15)
  }

```{r}
ggplot(dc, aes(x=TPACK, y=var, fill=studiested2)) + 
  geom_bar(stat="identity", position="dodge") +
  #scale_fill_manual(values=viridis(3)) + 
  geom_errorbar(aes(ymin=var-sd, ymax=var+sd), # se
                  linewidth=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
  ggtitle("PCK, TK og TPACK fordelt på studiested") +
  guides(fill="none") +
  # https://stackoverflow.com/questions/53843221/make-y-axis-start-at-1-instead-of-0-within-ggplot-bar-chart
#  coord_cartesian(ylim = c(1,5)) +
  ylab("verdi") +
  xlab("") +
  theme_bw() +
  facet_wrap(~studiested2)
```
